Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
added more sig vals; fixed sig format

% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
\subsubsection{Rewinds vs. Static Photos} 
Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$). When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time. Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind. As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues. Three participants who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind. They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on trip memory rather than location memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
%TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Location memorability and trip memorability are affected differently by frequency of visits (Table~\ref{table:betweensubjects}). Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited. The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study. In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, $p < 0.01$. This effect does not occur for trip memorability. In the most frequently visited places, trips are remembered 51\% of the time. Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%. Our study also shows that comparing to static street-view images, recollection of trip memories using Rewinds is significantly improved for least frequently taken trips by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

@@

\subsubsection{GPS Usage}
Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p = .0715 (<.1)$. 
% h - prob explain this a little bit more

% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance. (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - come back to this if time allows
% because memories are simply not encoded so there's no way to retrieve it in the first place?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1,179) = 8.734$, p = 0.0016 ($< 0.01$), but does not impose significant effects on trip remembrance $\chi^2(1,177) = 0.713$, p = 0.1992 ($> 0.05$).  When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time. Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%. Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, they may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations. One non-regular GPS user mentioned that ``I identify by landmarks'', yet this is something that regular GPS users may pay less attention to. \\

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.

@@

\subsubsection{GPS Usage}
% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
% GPS - 69%, non-GPS - 81%
Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did. Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them. The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations. Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations. Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory. So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory. One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.

@@

\subsubsection{Travel Companions}
% significant effects on photo/location belivability $\chi^2(1,91) = 20.956$, p < 0.01
% traveling alone - 82%, not alone - 25%
% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(1,127) = 1.865$, p = 0.086(< 0.1)
% traveling alone - 84%, not alone - 72%
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.

@@

\subsection{Frequent Travellers}
% no significant effects on photo desirability $\chi^2(1,179) = 0.828$, p = 0.1814(> 0.05)
% significant effects on video/trip desirability $\chi^2(1, 179) = 9.754$, p = 0.0009(< 0.01)
% frequent - 21 %, non-frequent - 2%
Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers. Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds. But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds. The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.

>>>>

% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
\subsubsection{Rewinds vs. Static Photos} 
Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos, $\chi^2(1, N=356) = 96.987$, $p <.01$. When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time. Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind. As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues. Three participants who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind. They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on trip memory rather than location memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
%TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Location memorability and trip memorability are affected differently by frequency of visits (Table~\ref{table:betweensubjects}). Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited. The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study. In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,N=128) = 14.458$, $p <.01$. This effect does not occur for trip memorability. In the most frequently visited places, trips are remembered 51\% of the time. Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%. Our study also shows that comparing to static street-view images, recollection of trip memories using Rewinds is significantly improved for least frequently taken trips by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

@@

\subsubsection{GPS Usage}
Our study also suggested that GPS users would benefit more from Rewinds, even though the difference was mildly significant by an increase about 15\%, $\chi^2(1, N=118) = 2.145$, $p =.0715 (<.1)$. 
% h - prob explain this a little bit more
% Our findings show that GPS usage significantly affect the rememberance of locations $\chi^2(1,179) = 8.734$, p < 0.01, but does not impose a siginificant effect on trip rememberance. (GPS users remember locations 33% of the time whereas non-GPS users remember locations 58% of the time)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - come back to this if time allows
% because memories are simply not encoded so there's no way to retrieve it in the first place?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our findings show that GPS usage significantly affect participants' remembrance of locations $\chi^2(1, N=179) = 8.734$, $p <.01$), but does not impose significant effects on trip remembrance $\chi^2(1, N=177) = 0.713$, $p >.05$).  When asked whether they remember the location in a static photo, non-regular GPS users gave a positive answer 58\% of the time whereas regular GPS users gave a positive answer 33\% of the time. Although the difference between non-regular and regular GPS users' trip remembrance is not statistically significance, the between-subject percentage values still lean towards the observation that it is perhaps easier for non-GPS users to recall episodic memories from external memory cues, given that the total trip remembrance rate for non-GPS users is 48\% and that of GPS users is 56\%. Since regular GPS users are frequently directed step-by-step on how to navigate through their environment, they may not need to pay as much attention to their surroundings, leading to potentially diminished locational awareness which could be the reason why regular GPS users had a lower remembrance rate for their ambience, particularly locations. One non-regular GPS user mentioned that ``I identify by landmarks'', yet this is something that regular GPS users may pay less attention to. \\

@@

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1, N=94) = 31.812$, $p <.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1, N=133) = 9.016$, $p <.01)$.

@@

\subsubsection{GPS Usage}
% no significant effects on location belivability $\chi^2(1,86) = 0.666$, p = 0.2073(> 0.05)
% signifant effects on trip belivability $\chi^2(1,128) = 2.917$, p = 0.0483(< 0.05)
% GPS - 69%, non-GPS - 81%
Our results show that participants who were non-regular GPS users found photos and Rewinds to be accurate to their memory more often than regular GPS users did in terms of percentage. Differences in Rewinds believability is statistically significant $\chi^2(1, N=128) = 2.917$, $p <.05$). Photos and Rewinds could only be considered accurate to a participant's memory if the participant first confirmed that they remembered the locations in them. The results in this section reflect percentages from a total pool of only photos and Rewinds that have remembered locations. Regular GPS users found 65\% of photos and 45\% of Rewinds accurate to their memory out of the photos and Rewinds in which they remembered the locations. Participants who did not regularly use GPS found 78\% of photos and 63\% of Rewinds accurate to their memory. So far, our findings show that regular GPS users remembered the locations in their digital memories less often, and from the locations they did remember, they were less likely to find a photo or Rewind accurate to their memory. One participant who identified as a regular GPS user said, ``I really don't pay attention to my surroundings when I'm driving. I'm focused on the GPS and the road,'' when asked about the accuracy of a trip.

@@

\subsubsection{Travel Companions}
% significant effects on photo/location belivability $\chi^2(1,91) = 20.956$, p < 0.01
% traveling alone - 82%, not alone - 25%
% significant effects on video/trip belivability if we use alpha = 0.1 - $\chi^2(1,127) = 1.865$, p = 0.086(< 0.1)
% traveling alone - 84%, not alone - 72%
Whether or not the participant was traveling alone during a trip is a significant predictor for whether the trip's associated Rewind will be kept. Rewinds in which the participant is traveling with another person make up about a fifth of all Rewinds in the entire study, but make up over half of the Rewinds that participants actually want to keep. Of Rewinds that participants judged desirable enough to keep, 39\% of were of trips in which the participant is traveling alone, and 54\% are of trips in which the participant is traveling with others. This difference is mildly significant $\chi^2(1, N=127) = 1.865$, $p <.1)$. The data shows clearly that a Rewind is considered more valuable if the trip it depicts was taken with company.

@@

\subsection{Frequent Travellers}
% no significant effects on photo desirability $\chi^2(1,179) = 0.828$, p = 0.1814(> 0.05)
% significant effects on video/trip desirability $\chi^2(1, 179) = 9.754$, p = 0.0009(< 0.01)
% frequent - 21 %, non-frequent - 2%
Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers. Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds. But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds. Although the effect on photo desirability is not siginificant, the difference is significant for Rewinds desirability, $\chi^2(1, N=179) = 9.754$, $p <.01$. The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.
